### 2014-03-15 src/analysis.Rnw
Change Title, Fix spellos

<<xpercentunit>>=
#1
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

@@

<<count>>=
#2
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel$operators <- 16 - o.xp.opsel$operators
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"

df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
@
\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
\label{fig:xroundsel}
\end{figure*}

>>>>

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

@@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

@@

% \begin{figure*}[t]
% <<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
% # o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
% # ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
% # 
% # o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
% # ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
% # 
% # o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
% # ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
% # 
% # o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
% # ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
% #   stat_boxplot(geom ='errorbar')+
% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
% @
% \caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
% \label{fig:xroundsel}
% \end{figure*}
%

% \begin{figure*}[t]
% <<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.opsel <- o.op.processed
% o.xp.opsel$operators <- 16 - o.xp.opsel$operators
% colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
% 
% df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
% qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
% @
% \caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
% \label{fig:xroundsel}
% \end{figure*}
%

### 2014-03-15 src/conclusion.Rnw
Change Title, Fix spellos

Our analysis suggests that simple random sampling --- that is, at the
project level --- works best when compared to more sophesticated schemes of
sampling. Further, we also note that random sampling performs better in
predicting final mutation score than operator selection.

This suggests that the best way to reduce the computational
requirements of mutation analysis is fortunately easy to apply in
almost any setting, given a tool that produces a good starting set of
mutants.  Namely, randomly sampling the total mutant population, even
with very small sample sizes, can effectively predict the results of
running all mutants, but at only a fraction of the computational cost.
Not only is this method simple and effective, but it is also quite
stable comapred to some alternatives, with a low standard deviation in
effectiveness across projects, for both original and random test suites.

>>>>

Our analysis suggests that simple random sampling --- that is, at the
project level --- works best when compared to more sophisticated schemes of
sampling. Further, we also note that random sampling performs better in
predicting final mutation score than operator selection.

This suggests that the best way to reduce the computational
requirements of mutation analysis is fortunately easy to apply in
almost any setting, given a tool that produces a good starting set of
mutants.  Namely, randomly sampling the total mutant population, even
with very small sample sizes, can effectively predict the results of
running all mutants, but at only a fraction of the computational cost.
Not only is this method simple and effective, but it is also quite
stable compared to some alternatives, with a low standard deviation in
effectiveness across projects, for both original and random test suites.

### 2014-03-15 src/introduction.Rnw
fix conflict
Change Title, Fix spellos

% 1. Describe the problem % 2. State your contributions
Mutation analysis is a method for evaluating the quality of test-suites. It
involves producing a family of \emph{mutants}, programs with small
differences from the original program, and evaluating the
effectiveness of test suites against these
mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus
introduced behave in a fashion similar to real faults, with respect to
the difficulty of detection.

@@

Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
relative merits of random sampling strategies and operator selection.
Random sampling can perform as well as or better than operator
selection, in these studies; a strategy of either program elements
based sample or one combining both program element-based sampling
and operator selection was best.
%{\bf ADG: did it combing random with pelem or pelem with operator???}

@@

We have attempted to rectify this situation with a large scale study
of real world programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 Java programs from Github, with size ranging from 50 LOC
to 100 KLOC, which allows widely applicable statistical inferences to
be made. We provide the results from running both original project
human generated test-suites and also automatically generated
test suites using random testing, increasing the applicability of our
findings to both testers in traditional development who are interested in applying mutation analysis to suite evaluation and to researchers who seek to compare test suites quickly.

@@

\item Our recommendations are valid for both testing researchers who
might be comparing automatically generated test-suites, and software
testers in real world development working to produce and evaluate manual test suites.

@@

%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}

%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
%and some that has been proposed by other researchers), and a some of the common operator selection
%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.

>>>>

% 1. Describe the problem % 2. State your contributions
Mutation analysis is a method for evaluating the quality of test suites. It
involves producing a family of \emph{mutants}, programs with small
differences from the original program, and evaluating the
effectiveness of test suites against these
mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus
introduced behave in a fashion similar to real faults, with respect to
the difficulty of detection.

@@

Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
relative merits of random sampling strategies and operator selection.
Random sampling can perform as well as or better than operator
selection, in these studies; a strategy of either program elements
based sample or one combining both program element-based sampling
and operator selection was best.

@@

We have attempted to rectify this situation with a large scale study
of real world programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 Java programs from Github, with size ranging from 50 LOC
to 100 KLOC, which allows widely applicable statistical inferences to
be made. We provide the results from running both original project
human generated test suites and also automatically generated
test suites using random testing, increasing the applicability of our
findings to both testers in traditional development who are interested in applying mutation analysis to suite evaluation and to researchers who seek to compare test suites quickly.

@@

\item Our recommendations are valid for both testing researchers who
might be comparing automatically generated test suites, and software
testers in real world development working to produce and evaluate manual test suites.

@@

%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}

%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%generated test suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
%and some that has been proposed by other researchers), and a some of the common operator selection
%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.
